Gravitational Lens Modeling of Flux Ratio Anomalous System B1555+375

### 2015-01-24 papers/B1555_EdgeOn/B1555_letter.tex
new model parameters update

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this information, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk(SIE+Expdisk). The second model
consists of two SIE mass profiles, for bulge and disk
respectively. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

@@

%%table1
\begin{table}
\begin{center}
\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
\begin{tabular}{ccccccc}
%%\tableline\tableline
		&SIE+Expdisk& 2-SIE		   
\\
\tableline\tableline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$93.74$ &	$81.67$	  \\
$M_{tot} / \sigma_2$& $1.19\times 10^{10} $  &$69.91$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\tableline

>>>>

\section{Lens Modeling}
To model B1555+375, we use the lens modeling code {\tt glafic}
\citep{Oguri}.  The inputs to the model are the observed image positions
and flux densities measured by the radio observations of \citet{Marlow}.
These authors present a singular isothermal ellipsoid (SIE) model that
provides the first fit to the image positions but
does not reproduce the strong flux ratio anomaly between components A and B.
(see Fig.6, Table 2 \& 3 in \citet{Marlow}). In K-band
image (Fig. 1, left), a recognizable edge-on disk is lie in the center
with position angle $~10$ degree. With this information, we model
B1555+375 with two models. The first model consists of an SIE bulge
and an exponential edge-on disk (SIE+Expdisk). The second model
consists of two SIE mass profiles (2-SIE), for bulge and disk
respectively. The full best-fit parameters are shown in Table 1. Both
of these models predict fairly matched results with the radio
observation. The comparison of observation and SIE+Expdisk result is
in Figure 2, Table 2 \& 3.
%These authors present a singular isothermal ellipsoid (SIE) model that
%provides an excellent fit to the image positions (?? IS THIS TRUE?--NO we get a better model result)

@@

%%table1
\begin{table}
\begin{center}
\caption{Lens Model Best-Fit Parameters.\label{tbl-1}}
\begin{tabular}{ccccccc}
%%\tableline\tableline
		&SIE+Expdisk& 2-SIE		   
\\
\tableline\tableline
$x_1$  	& $-0.1883$	& $-0.1809$	  \\
$y_1$	&$-0.1923$	&$-0.1702$	  \\
$x_2$	&$-0.1615$ 	&$-0.1592$	  \\
$y_2$	&$-0.2502$	& $-0.1833$	  \\
$\sigma_1$	&$92.90$ &	$95.05$	  \\
$M_{tot} / \sigma_2$& $1.17\times 10^{10} $  &$81.36$ 	 \\  
$e_1$	& $0.27$	& $0.27$ \\  
$\theta_1$	&$105.5 \degr$ & $97.7 \degr$	 \\
$e_2$	&$0.84$	&$0.83$      \\
$\theta_2$	&$7.4\degr$ &$7.4\degr$  \\
$r_e$	& $0.20 ''$ &  -- \\
\tableline
